Some Fancy Title

### 2023-10-03 output/paper/sections/methods.qmd
Working on structure of paper. Issues with cross-referencing tables in Quarto.
Just checking pipeline works.

- Methods for selecting potential confounders (provide DAGs).
- Describe all statistical methods with assumptions, including those used to control for confounding.
- Describe any methods used to examine subgroups and interactions.
- Explain how missing data were addressed.
- Cohort study: explain how loss to follow-up was addressed.
- Cross-sectional study: describe analytical methods taking account of sampling strategy.
- Describe any sensitivity analyses.
- When referring to previous publications for methods' details, include a brief description of the approach, key assumptions and limitations, and any deviation.
- Names and version numbers for the used software packages, including non-data arguments if deviating from the default ones.

>>>>

- Methods for selecting potential confounders (provide DAGs).
- Describe all statistical methods with assumptions, including those used to control for confounding.
  - Description of outcome model, weighting method, estimand, and balance assessment.
  - Description of method used to estimate effects (e.g., g-computation).
  - Description of method used for SE and CI.
- Describe any methods used to examine subgroups and interactions (sub-group analysis or moderation analysis or analysis of effect-modification).
- Explain how missing data were addressed.
- Cohort study: explain how loss to follow-up was addressed.
- Cross-sectional study: describe analytical methods taking account of sampling strategy.
- Describe any sensitivity analyses.
- When referring to previous publications for methods' details, include a brief description of the approach, key assumptions and limitations, and any deviation.
- Names and version numbers for the used software packages, including non-data arguments if deviating from the default ones.
